%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{DDS IT} % Organization
{Senior Site Reliability Engineer} % Job title
{Auckland, New Zealand} % Location
{Nov. 2022 - Present | 2 yrs 11 mos} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Used Terraform to manage all Azure infrastructure for multiple customers.}
\item {Architected and operated several Azure Kubernetes Service (AKS) clusters.}
\item {Mentored team members, fostering a culture of continuous improvement and increased customer value.}
\item {Led the response to high-priority incidents.}
\item {Automated manual processes, resulting in hundreds of saved hours per year.}
\end{cvitems}
}
%------------------------------------------------

\cventry
{Westpac New Zealand} % Organization
{Senior Platform Engineer} % Job title
{Auckland, New Zealand} % Location
{Jan. 2022 - Nov. 2022 | 11 mos} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Designed and implemented a PagerDuty solution to enhance the on-call experience for engineers.}
\item {Improved deployment pipelines for Kubernetes-based Apple Pay and Google Pay applications.}
\item {Played a key role in migrating nodes to an upgraded Chef server.}
\item {Provided on-call support for the card transactions platform, ensuring operational excellence.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{LearnCoach} % Organization
{DevOps Engineer (Freelance)} % Job title
{Auckland, New Zealand} % Location
{Jan. 2022 - Mar. 2024 | 2 yrs 2 mos} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Supporting infrastructure maintenance, upgrades and security enhancements.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{International Volunteer HQ} % Organization
{DevOps Engineer (Freelance)} % Job title
{Auckland, New Zealand} % Location
{Dec. 2020 - Nov. 2023 | 3 yrs} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Supporting infrastructure maintenance, upgrades and security enhancements.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{LearnCoach} % Organization
{DevOps Engineer} % Job title
{Auckland, New Zealand} % Location
{Jul. 2020 - Jan. 2022 | 1 yr 7 mos} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Re-architected application infrastructure to enhance reliability and scalability.}
\item {Migrated the team to a container-based application release process, streamlining deployments.}
\item {Implemented a CI/CD system with GitHub Actions, saving hundreds of developer hours monthly.}
\item {Introduced Terraform and Ansible to encourage versioning and automated management of all core system components.}
\item {Developed a comprehensive monitoring solution using Prometheus, Grafana, and Loki.}
\item {Reduced time to set up a development environment by 95\%.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{International Volunteer HQ} % Organization
{DevOps Engineer} % Job title
{Auckland, New Zealand} % Location
{Jul. 2018 - Jun. 2020 | 2 yrs} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Conducted a comprehensive audit of AWS architecture, enhancing security and resilience while reducing costs by over 30\%.}
\item {Containerised core applications using Docker, significantly improving developer effectiveness and deployment speed.}
\item {Developed a CI/CD pipeline with Jenkins, cutting test suite run time by 75\% and streamlining the development process.}
\item {Established incident alerting and on-call scheduling through PagerDuty, ensuring prompt response to system issues.}
\item {Used Ansible to completely reimplement deprecated configuration management tooling.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Orion Health} % Organization
{Solution Engineer} % Job title
{Auckland, New Zealand} % Location
{Jan. 2015 - Jul. 2018 | 3 yrs 7 mos} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Project: Unison (Consult \& Coordinate)}
\item {Created, managed and monitored AWS environments.}
\item {Utilised Bamboo to develop a CI/CD pipeline.}
\item {Automated instance configuration using tools such as Puppet and }Ansible.
\item {Provided technical support for a range of applications and }systems.
\item {Reviewed project contributions to ensure delivery of high quality }solutions.
\item {On-boarded and trained new team members.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Orion Health} % Organization
{Graduate Implementation Consultant} % Job title
{Auckland, New Zealand} % Location
{Jan. 2014 - Jan. 2015 | 1 yr 1 mo} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Project: ACT Walk in Centre}
\item {Project: Oracle eGate Migration to Rhapsody}
\item {Provided technical support for a range of applications and systems.}
\item {Implemented decision making algorithms to assist in the triaging of in-patients.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{The Photon Factory (The University of Auckland)} % Organization
{Researcher} % Job title
{Auckland, New Zealand} % Location
{Nov. 2012 - Feb. 2013 | 4 mos} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Researched existing microfabrication and injection moulding techniques.}
\item {Developed prototypes suitable for use in the production of microfluidic devices.}
\item {Presented findings to interested parties.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
